---
title: "Startup Incubation Outcomes: A Fuzzy-Set QCA of Campus Founders"
author: ""
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    toc_float: true
    toc_depth: 3
    number_sections: true
    theme: flatly
    df_print: paged
---

```{r setup, echo=FALSE, message=FALSE, warning=FALSE}
library(QCA)
library(knitr)
library(kableExtra)
library(ggplot2)
library(dplyr)

knitr::opts_chunk$set(
  echo    = FALSE,
  message = FALSE,
  warning = FALSE,
  fig.align = "center",
  fig.width = 9,
  fig.height = 5,
  dpi = 150
)

# APA-style kable for HTML
fmt_tbl <- function(x, caption, digits = 3) {
  kable(x, digits = digits, caption = caption, format = "html") %>%
    kable_styling(
      bootstrap_options = c("striped", "hover", "condensed", "bordered"),
      full_width  = FALSE,
      font_size   = 13,
      position    = "center"
    )
}

# Extract data frame from any QCA result object
qca_df <- function(x) {
  if (!is.null(x$IC) && !is.null(x$IC$incl.cov) &&
      is.data.frame(x$IC$incl.cov))   return(x$IC$incl.cov)
  if (!is.null(x$incl.cov) && is.data.frame(x$incl.cov))
                                        return(x$incl.cov)
  if (is.data.frame(x))                 return(x)
  data.frame(Output = capture.output(print(x)), stringsAsFactors = FALSE)
}

# Extract data frame from a QCA_tt truth-table object
tt_df <- function(x) {
  raw <- tryCatch({
    lst <- unclass(x)
    if (is.list(lst) && is.data.frame(lst$tt)) lst$tt else NULL
  }, error = function(e) NULL)
  if (!is.null(raw)) return(raw)
  if (is.data.frame(x)) return(x)
  data.frame(Output = capture.output(print(x)), stringsAsFactors = FALSE)
}

# Parse solution terms from a QCA_min object for Figure 3
sol_terms <- function(sol) {
  terms <- unlist(sol$solution, recursive = TRUE, use.names = FALSE)
  terms <- terms[is.character(terms)]
  terms <- trimws(unlist(strsplit(terms, "\\+")))
  unique(terms[nzchar(terms)])
}

# Compute fuzzy AND (minimum) membership for a solution term
term_membership <- function(data, term) {
  parts <- trimws(unlist(strsplit(term, "\\*")))
  mlist <- lapply(parts, function(p) {
    p     <- gsub("`", "", p, fixed = TRUE)
    neg   <- grepl("^~", p)
    cname <- sub("^~", "", p)
    if (!cname %in% names(data)) return(rep(NA_real_, nrow(data)))
    v <- data[[cname]]
    if (neg) 1 - v else v
  })
  if (!length(mlist)) return(rep(NA_real_, nrow(data)))
  do.call(pmin, c(mlist, na.rm = FALSE))
}

apa_theme <- theme_classic(base_size = 12) +
  theme(panel.grid    = element_blank(),
        strip.background = element_blank(),
        strip.text    = element_text(face = "bold"),
        legend.position = "bottom")
```

# 1. Setup and Data

```{r load_data}
d <- read.csv("../data/processed/qca_calibrated.csv",
              row.names = "startup_id")
```

The analytic sample contains **`r nrow(d)` startups**: `r sum(d$decision=="Accepted")` accepted and `r sum(d$decision=="Rejected")` rejected cases from Campus Founders batches 3–5. All fuzzy set memberships range from 0 (full non-membership) to 1 (full membership), with the 0.5 crossover representing theoretical ambiguity.

# 2. Calibration

```{r calibrate}
# BERTopic raw topic shares are all below 0.5 — recalibrate with direct method
d$T_testing_f  <- calibrate(d$T_testing,  type="fuzzy", method="direct",
                             thresholds=c(0.0085, 0.0286, 0.0635))
d$T_customer_f <- calibrate(d$T_customer, type="fuzzy", method="direct",
                             thresholds=c(0.0386, 0.0859, 0.1812))
d$T_market_f   <- calibrate(d$T_market,   type="fuzzy", method="direct",
                             thresholds=c(0.0283, 0.0619, 0.1341))
d$T_revenue_f  <- calibrate(d$T_revenue,  type="fuzzy", method="direct",
                             thresholds=c(0.0141, 0.0578, 0.1402))

conds_core <- c("PA_fuzzy","SF_fuzzy","TGB_f","TGT_f","TGR_f",
                "TEAM_f","PLAT_f","B2B_f")
conds_ext  <- c("PA_fuzzy","SF_fuzzy","TGT_f","TGR_f",
                "TEAM_f","PLAT_f","T_testing_f")
```

## Table 1: Descriptive statistics of all fuzzy conditions

```{r table01}
all_conds <- c(conds_core,
               "T_testing_f","T_customer_f","T_market_f","T_revenue_f")
desc <- data.frame(
  Condition = all_conds,
  Min  = sapply(d[all_conds], min,  na.rm=TRUE),
  Mean = sapply(d[all_conds], mean, na.rm=TRUE),
  Max  = sapply(d[all_conds], max,  na.rm=TRUE),
  SD   = sapply(d[all_conds], sd,   na.rm=TRUE),
  n_above_0.5 = sapply(d[all_conds], function(x) sum(x >= 0.5)),
  row.names = NULL
)
fmt_tbl(desc,
  "Table 1. Descriptive Statistics of Calibrated Fuzzy Conditions (N = 70)")
```

## Figure 1: Distribution of PA and SF by decision

```{r figure01, fig.cap="Figure 1. Distribution of PA and SF fuzzy scores by acceptance decision."}
fig1 <- rbind(
  data.frame(Score=d$PA_fuzzy, Condition="Problem Articulation (PA)",
             Decision=d$decision),
  data.frame(Score=d$SF_fuzzy, Condition="Solution Fit (SF)",
             Decision=d$decision)
) %>% count(Condition, Score, Decision)

ggplot(fig1, aes(x=factor(Score), y=n, fill=Decision)) +
  geom_col(position="dodge", colour="black", linewidth=0.2) +
  facet_wrap(~Condition, scales="free_x") +
  scale_fill_grey(start=0.25, end=0.75) +
  labs(x="Fuzzy score", y="Number of startups", fill="Decision") +
  apa_theme
```

## Figure 2: Outcome distributions

```{r figure02, fig.cap="Figure 2. Distribution of the Z&Z belief-challenge ladder outcome. The dashed line marks the 0.5 QCA crossover."}
ggplot(d, aes(x=OUTCOME_ladder, fill=decision)) +
  geom_histogram(binwidth=0.1, boundary=0,
                 position="identity", alpha=0.65, colour="black") +
  geom_vline(xintercept=0.5, linetype="dashed", linewidth=0.8) +
  annotate("text", x=0.68, y=Inf, vjust=2, size=3.8,
           label=sprintf("n = %d above 0.5", sum(d$OUTCOME_ladder > 0.5))) +
  scale_fill_grey(start=0.25, end=0.75) +
  labs(x="Feedback challenge ladder membership",
       y="Count of startups", fill="Decision") +
  apa_theme
```

# 3. Analysis A — Acceptance Outcome

## 3.1 Necessity Analysis

```{r nec_accept}
nec_a <- superSubset(d, outcome="OUTCOME_accept", conditions=conds_core,
                     relation="necessity", incl.cut=0.90, cov.cut=0.50)
```

```{r table02}
fmt_tbl(qca_df(nec_a),
  "Table 2. Necessity Analysis: Acceptance Outcome (incl.cut = 0.90, cov.cut = 0.50)")
```

## Figure 3: Necessity XY plots

```{r figure03, fig.height=7, fig.cap="Figure 3. Necessity XY plots for the eight core conditions. Cases above the diagonal indicate the condition is a subset of the outcome."}
fig3 <- do.call(rbind, lapply(conds_core, function(cn) {
  data.frame(Condition=cn, Membership=d[[cn]],
             Outcome=d$OUTCOME_accept, Decision=d$decision)
}))
ggplot(fig3, aes(x=Membership, y=Outcome, colour=Decision)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", colour="black") +
  geom_point(alpha=0.7, size=1.8) +
  geom_smooth(method="loess", se=FALSE, linewidth=0.6) +
  facet_wrap(~Condition, ncol=4) +
  coord_equal(xlim=c(0,1), ylim=c(0,1)) +
  scale_colour_grey(start=0.1, end=0.65) +
  labs(x="Condition membership", y="Acceptance membership",
       colour="Decision") +
  apa_theme
```

## 3.2 Truth Table

```{r tt_accept}
tt_accept <- truthTable(d, outcome="OUTCOME_accept", conditions=conds_core,
                        incl.cut=0.80, n.cut=1,
                        show.cases=TRUE, sort.by="incl,n")
```

```{r table03}
fmt_tbl(tt_df(tt_accept),
  "Table 3. Truth Table: Acceptance Outcome (incl.cut = 0.80, n.cut = 1)")
```

## 3.3 Parsimonious Solution

```{r sol_pars}
sol_pars <- QCA::minimize(tt_accept, details=TRUE, include="?")
```

```{r table04}
fmt_tbl(qca_df(sol_pars),
  "Table 4. Boolean Minimization: Parsimonious Solution — Acceptance Outcome")
```

## 3.4 Intermediate Solution

```{r sol_inter}
sol_inter <- QCA::minimize(tt_accept, details=TRUE, include="?",
  dir.exp=list(PA_fuzzy=1, SF_fuzzy=1, TGB_f=1, TGT_f=1,
               TGR_f=1, TEAM_f=1, PLAT_f=1, B2B_f=1))
```

```{r table05}
fmt_tbl(qca_df(sol_inter),
  "Table 5. Boolean Minimization: Intermediate Solution — Acceptance Outcome")
```

## Figure 4: Sufficiency XY plots for solution paths

```{r figure04, fig.cap="Figure 4. Sufficiency XY plots for intermediate solution paths. Cases labeled more than 0.2 from the diagonal are deviant cases."}
terms <- sol_terms(sol_inter)
if (length(terms) == 0) terms <- "No_solution"

fig4 <- do.call(rbind, lapply(terms, function(tm) {
  memb <- term_membership(d, tm)
  data.frame(startup=rownames(d), Solution=tm,
             Membership=memb, Outcome=d$OUTCOME_accept,
             Decision=d$decision,
             Outlier=abs(memb - d$OUTCOME_accept) > 0.2)
}))

ggplot(fig4, aes(x=Membership, y=Outcome, colour=Decision)) +
  geom_abline(slope=1, intercept=0, linetype="dashed", colour="black") +
  geom_point(alpha=0.8, size=2) +
  ggrepel::geom_text_repel(
    data=subset(fig4, Outlier),
    aes(label=startup), colour="black",
    size=2.8, max.overlaps=20) +
  facet_wrap(~Solution) +
  coord_equal(xlim=c(0,1), ylim=c(0,1)) +
  scale_colour_grey(start=0.1, end=0.65) +
  labs(x="Solution-term membership", y="Acceptance membership",
       colour="Decision") +
  apa_theme
```

## 3.5 Rejection Paths

```{r rej_paths}
d$REJ <- 1 - d$OUTCOME_accept
tt_rej <- truthTable(d, outcome="REJ", conditions=conds_core,
                     incl.cut=0.80, n.cut=1,
                     show.cases=TRUE, sort.by="incl,n")
sol_rej <- QCA::minimize(tt_rej, details=TRUE, include="?")
```

```{r table06}
fmt_tbl(qca_df(sol_rej),
  "Table 6. Boolean Minimization: Rejection Paths (~OUTCOME_accept)")
```

# 4. Analysis B — Feedback Challenge Ladder

## 4.1 Necessity Analysis

```{r nec_ladder}
nec_b <- superSubset(d, outcome="OUTCOME_ladder", conditions=conds_core,
                     relation="necessity", incl.cut=0.85, cov.cut=0.40)
```

```{r table07}
fmt_tbl(qca_df(nec_b),
  "Table 7. Necessity Analysis: Feedback Challenge Ladder (incl.cut = 0.85)")
```

## 4.2 Truth Table and Sufficiency

```{r ladder_suf}
tt_ladder  <- truthTable(d, outcome="OUTCOME_ladder", conditions=conds_core,
                         incl.cut=0.75, n.cut=1,
                         show.cases=TRUE, sort.by="incl,n")
sol_ladder <- QCA::minimize(tt_ladder, details=TRUE, include="?")
```

```{r table08}
fmt_tbl(qca_df(sol_ladder),
  "Table 8. Sufficiency Analysis: Feedback Challenge Ladder")
```

## 4.3 Endorsing Feedback Paths

```{r endorse_paths}
d$ENDORSE <- 1 - d$OUTCOME_ladder
tt_end <- tryCatch(
  truthTable(d, outcome="ENDORSE", conditions=conds_core,
             incl.cut=0.80, n.cut=1,
             show.cases=TRUE, sort.by="incl,n"),
  error = function(e) NULL
)
sol_end <- if (!is.null(tt_end)) {
  tryCatch(QCA::minimize(tt_end, details=TRUE, include="?"),
           error = function(e) NULL)
} else {
  NULL
}
```

```{r table09}
if (!is.null(sol_end)) {
  fmt_tbl(qca_df(sol_end),
    "Table 9. Boolean Minimization: Endorsing Feedback Paths (~OUTCOME_ladder)")
} else {
  cat("*No unique minimization found for endorsing paths — all configurations used.*")
}
```

# 5. Analysis C — Robustness with BERTopic T_testing

## 5.1 Necessity of T_testing_f

```{r c1_nec}
pof_test <- pof(setms=d[,"T_testing_f",drop=FALSE],
                outcome="OUTCOME_accept", data=d, relation="necessity")
```

```{r table10}
fmt_tbl(qca_df(pof_test),
  "Table 10. Necessity Analysis: BERTopic Testing Condition (T_testing_f)")
```

## 5.2 Extended Truth Table and Minimization

```{r ext_tt}
tt_ext  <- truthTable(d, outcome="OUTCOME_accept", conditions=conds_ext,
                      incl.cut=0.80, n.cut=1,
                      show.cases=TRUE, sort.by="incl,n")
sol_ext <- QCA::minimize(tt_ext, details=TRUE, include="?")
```

```{r table11}
fmt_tbl(qca_df(sol_ext),
  "Table 11. Robustness Check: Extended Conditions Including T_testing_f")
```

# 6. Summary

## Table 12: Per-condition necessity consistency and coverage

```{r table12}
summ <- do.call(rbind, lapply(c(conds_core, "T_testing_f"), function(cn) {
  r  <- pof(setms=d[,cn,drop=FALSE], outcome="OUTCOME_accept",
            data=d, relation="necessity")
  nms <- names(r$incl.cov)
  ci  <- if ("incl"  %in% nms) "incl"  else "inclN"
  cv  <- if ("cov.r" %in% nms) "cov.r" else "covN"
  data.frame(Condition=cn,
             Consistency=r$incl.cov[[ci]],
             Coverage   =r$incl.cov[[cv]])
}))
row.names(summ) <- NULL

fmt_tbl(summ,
  "Table 12. Per-Condition Necessity Consistency and Coverage (OUTCOME_accept)")
```

## Figure 5: Condition profiles by decision

```{r figure05, fig.height=6, fig.cap="Figure 5. Mean fuzzy set membership for each core condition, split by acceptance decision."}
fig5 <- d %>%
  select(decision, all_of(conds_core)) %>%
  tidyr::pivot_longer(-decision,
                      names_to="Condition",
                      values_to="Membership") %>%
  group_by(decision, Condition) %>%
  summarise(Mean=mean(Membership), SE=sd(Membership)/sqrt(n()), .groups="drop")

ggplot(fig5, aes(x=Condition, y=Mean, fill=decision)) +
  geom_col(position=position_dodge(0.7), width=0.65,
           colour="black", linewidth=0.2) +
  geom_errorbar(aes(ymin=Mean-SE, ymax=Mean+SE),
                position=position_dodge(0.7), width=0.25) +
  scale_fill_grey(start=0.25, end=0.75) +
  scale_y_continuous(limits=c(0,1)) +
  geom_hline(yintercept=0.5, linetype="dashed", colour="grey40") +
  labs(x="Condition", y="Mean fuzzy membership ± SE", fill="Decision") +
  apa_theme +
  theme(axis.text.x=element_text(angle=35, hjust=1))
```
